Improving content discovery through combining linked data and data mining techniques

### 2016-05-05 report/chapters/02-background.tex
Bit more for chapter 2

\subsection{Data Fragmentation in Organisations}
\subsection{Enterprise Integration}
\subsection{Organisational Difficulties with Enterprise Integration}
\label{sec:ei-difficulties}
\subsection{Linked Enterprise Data}

>>>>

At the end of chapter~\ref{chp:intro}, there is some discussion of the
benefits of using semantics and linked data for any process that we wish
to apply across the entire corpus.

In this section, the goal is to strengthen that case and review other
previous work around using linked data in the enterprise. This is a more
general argument for any enterprise with data (e.g. internal information
about staff or business processes) and not just media orgainisations.

\subsection{Data Fragmentation in Organisations}

The first thing to highlight is why enterprises struggle to work with all
the data spread across the organisation. Where all interesting data is
contained in a single database, it is relatively simple to develop software
that extracts all that data in a single query and processes it in some way.

It is rare, however, for any large business to keep all data stored in
one location and in one format. Even fairly simple businesses will have
separate data stores for their employee data, for example, and all
usernames and passwords for the corporate email system. Without much effort,
a business that implements or purchases two distinct systems for personnel
and email has already fragmented its data.

There may be no difficulty from this initially, but then a problem arises
where it is noted that employees, in this example, do not automatically have
their email accounts disabled when they leave the organisation. Smaller
businesses might simple employ adminstrative staff to keep databases in
sync and implement a standard process to handle the case of an employee
leaving the company.

In a large organisation, it may be more desirable to automate this. This then
steps into the field of \emph{Enterprise Integration}, discussed in the next
section.

In a media organisation, it might be argued that whilst all employee and
internal systems data is in bespoke systems, we can ensure all ``content''
is stored in a single system such as a \emph{content management system}. This
can be strained by at least three different pressures:

\begin{enumerate}
\item diversity of content;
\item technology refresh cycles; and
\item fragmentation of teams.
\end{enumerate}

Where an organisation produces multiple \emph{types} of content, it
may be the case that one system is optimised for writing and editing textual
articles (e.g. news) and another system is purchased or created to handle
video content. If these systems are built by different teams or, worse,
are procured independently as commercial offerings, there is little incentive
for the content to be compatible for generalising techniques such as search
or data mining.

This is the compounded where development teams decide to rebuild software
systems to keep up to date with changes in the industry, implement new features
in ways not made possible by the old system or because the old system is
becoming more expensive to maintain than it is to replace. This also applies
for buying in new systems because a contract was up for renewal and the fresh
procurement process chose a competitor's commercial offering which is
incompatible than that of the previous provider.

When this happens, the teams might choose to migrate all the old content to
the system, but they also might choose not to if the older system is still
running without issues. If it can continue to serve old content in a
"read-only" state without issues, then there may not be a strong business
case to migrate that old content as long as it continues to work.

The teams may also choose to archive the old content in a flat state not
intended for editing. This allows the old system to be decommissioned, but it
does leave older content in a format not easily queries and certainly not
compatible with how newer content is actively managed.

The final problem highlighted above -- that of fragmentation of teams in the
organisation -- particularly affects very large enterprises such as the BBC.
Any media company might find that content production teams work best when
given sufficient autonomy. A consequence of this is that multiple teams
might implement very similar solutions to the same problems, but without the
incentive to share nor unify their approaches. From this, we can ultimately
end up with multiple content management systems even for the same type of
content, all actively maintained.

A lot of this falls out of what was observed by
Conway\cite{conway1968committees} (sometimes as known as \emph{Conway's Law})
in that an organisation's architecture ends up reflecting its communication
structures. From this, we can assume that if two teams in an organisation
are not encouraged to communicate well and often, then they are less likely to
share software code and data systems.

\subsection{Enterprise Integration}
\subsection{Organisational Difficulties with Enterprise Integration}
\label{sec:ei-difficulties}
\subsection{Linked Enterprise Data}
